edgeR

### 2019-08-27 analysis/09_egdeR.Rmd
first pass works

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(edgeR)
library(org.Gg.eg.db)
```

# edgeR: differential expression analysis of digital gene expression data

https://www.bioconductor.org/packages/release/bioc/vignettes/edgeR/inst/doc/edgeRUsersGuide.pdf

## quick start

```{r}
x <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
group <- colData$treatment

y <- DGEList(counts=x,group=group)
y <- calcNormFactors(y)
design <- model.matrix(~group)
y <- estimateDisp(y,design)

# To perform quasi-likelihood F-tests:
fit <- glmQLFit(y,design)
qlf <- glmQLFTest(fit,coef=2)
topqlf <- as.data.frame(topTags(qlf))

topqlf$entrezid <- row.names(topqlf)
left_join(topqlf, geneinfo, by = "entrezid")
```
